---
title: "HW5 notebook"
output: html_notebook
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r warning=FALSE}
library(tmap)
library(tmaptools)
library(rgdal)
library(sp)
library(OpenStreetMap)
library(osmdata)

myShapeInR<-readOGR(dsn="mygeodata/NavyaDass_Chittoor_HW3.shp")
myPointsInR <- read_osm(bbox(myShapeInR))
tm_shape(myPointsInR) + tm_raster() + tm_shape(myShapeInR) + tm_dots(size=0.5,col="red")

```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

```{r}
library(ggmap)
library(PBSmapping)

myShapeInRg = importShapefile("mygeodata/NavyaDass_Chittoor_HW3")
DataFrame <- as.data.frame(myShapeInRg)
Map <- get_map(location = c(lon=-118.286175 , lat=34.021887),source = "google", zoom = 15)
ggmap(Map) + geom_point(data=DataFrame, aes(x=X, y=Y), size=2, color="red")
```


